---
title: "p8105_hw5_ly2565"
author: "Lin Yang"
date: "11/11/2021"
output: github_document
---

```{r, setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

### Load and describe the raw dataset

```{r, message = FALSE}
homicide_raw = read_csv("data/homicide-data.csv")
```
This raw homicide dataset contains `r nrow(homicide_raw)` observations of `r ncol(homicide_raw)` variables: `r names(homicide_raw)`.

### Clean the dataset

Summarize total number of homicides and the number of unsolved homicides within cities.
```{r, message = FALSE}
homicide_df = 
  homicide_raw %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition != "Closed by arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")) %>% 
  filter(city_state != "Tulsa, AL") %>% 
  relocate(city_state) %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    total = n())

homicide_df
```

### Proportion of unsolved homicides

Run `prop.test` for Baltimore, MD.
```{r}
baltimore_summary = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

baltimore_test =
  prop.test(
    pull(baltimore_summary, unsolved), 
    pull(baltimore_summary, total)) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))

baltimore_test
```

Run `prop.test` for each city.
```{r}
homicide_test =
  homicide_df %>%
  mutate(
    test_results = map2(unsolved, total, prop.test),
    tidy_results = map(test_results, broom::tidy)) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

homicide_test
```

Scatterplot showing the estimates and CIs for each city.

```{r, dpi = 300, echo=FALSE}
homicide_test %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate, color = city_state)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "none") +
  labs(
    x = "City",
    y = "Estimated Proportion of Unsolved Homicides",
    title = "Estimated Proportion of Unsolved Homicides in Each City"
  )
```


## Problem 2

Create a tidy dataframe containing data from all participants.
```{r, message = FALSE}
df = tibble(
  file = list.files("data/data2")) %>% 
  mutate(
    id = str_remove(file, ".csv"),
    path = str_c("data/data2/", file),
    data = map(path, read_csv)) %>% 
  unnest(data) %>% 
  select(-file, -path) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  ) %>% 
  separate(id, into = c("group", "id"))

df
```

Make a spaghetti plot showing observations on each subject over time.
```{r, dpi = 300}
df %>% 
  ggplot(aes(x = week, y = observation, group = interaction(group, id), color = group)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  labs(
    x = "Week",
    y = "Observations",
    title = "Observations on Each Subject Over Time",
    color = "Group"
  )
```
Based on the plot, observations on participants from the experimental arm increase over time, whereas the control arm doesn't seem to have a significant difference in overall. Starting from week 2, observations from the experimental arm are generally higher than the control arm. 

## Problem 3

Load the iris dataset and introduce some missing values.
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function that takes a vector as an argument and replaces missing values.\
For numeric variables, fill in missing values with the mean of non-missing values;\
For character variables, fill in missing values with "Virginica".

```{r}
fill_na = function(vec) {
  if (is.numeric(vec)) {
    vec = replace_na(vec, mean(vec, na.rm = TRUE))
  }
  if (is.character(vec)) {
    vec = replace_na(vec, "Virginica")
  }
  
  vec
}
```

Apply this function to the dataframe `iris_with_missing` to get a dataframe without missing values.
```{r, warning = FALSE}
iris_no_missing = map(iris_with_missing, fill_na) %>% 
  as.tibble()

iris_no_missing
```







